---
title: "Kermit Perceptions Ranked Based Test"
author: "Corinna Hong"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is Corinna's first message

Hi! This is Camila, so glad this is all working!

Woohoo! Teamwork makes the dream work

```{r}
library(tidyverse)
kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre))+
  geom_histogram(bins = 4)+
  facet_wrap(~Gender)

kermit_hist

```

Perform rank-based comparisons using Mann-Whitney U and Wilcoxon Signed Ranked.

Is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}

# Ho: There is NOT a significant differnece in ranks for male and female respondents.
# HA: There is a significant difference in ranks for male and female respondents.

mwu_kermit <- kermit %>%
  wilcox.test(Score.pre ~ Gender, data =.) # Default is a Mann-Whitney U for unpaired data
mwu_kermit

```
"There was no significant difference in ranks for male and female respondents (W = 155.5, p = 0.4, alpha = 0.05)"

Next question (Camila):

Is there a significant change in kermit rankings before and after his Bren talk?

```{r}
#H0: There is not a signficant difference in ranks for pre- and post- talk scores
wsr_kermit <- wilcox.test(kermit$Score.pre, kermit$Score.post, paired = TRUE)

wsr_kermit

```
There is no significant difference in ranks for pre- and post-talk kermit scores (statistical summary here...)

